(working title) Local Physiological Adaptation in \textit{Mimulus cardinalis}

### 2015-04-29 ms/ms.tex
Worked on Resuls and Discussion.

\documentclass[11pt, oneside]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

%
% Start document
%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\maketitle
\listoffigures
\listoftables

@@

\subsection*{Principal components of germination, growth, and photosynthesis}
[maybe this goes in Results?]
We summarized population-level coefficients, after factoring out Treatment and other effects, using principal components. Spec
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
  \hlstd{popMeans} \hlkwb{<-} \hlkwd{data.frame}\hlstd{(}
    \hlkwc{germ} \hlstd{=} \hlkwd{c}\hlstd{(}\hlkwd{coef}\hlstd{(fitGerm)[}\hlnum{1}\hlstd{],} \hlkwd{coef}\hlstd{(fitGerm)[}\hlnum{1}\hlstd{]} \hlopt{+} \hlkwd{coef}\hlstd{(fitGerm)[}\hlnum{2}\hlopt{:}\hlnum{16}\hlstd{]),}
    \hlkwc{LER} \hlstd{= fitLER}\hlopt{$}\hlstd{lsmeans.table[}\hlnum{1}\hlopt{:}\hlnum{16}\hlstd{,} \hlstr{"Estimate"}\hlstd{],}
    \hlkwc{SER} \hlstd{= fitSER}\hlopt{$}\hlstd{lsmeans.table[}\hlnum{1}\hlopt{:}\hlnum{16}\hlstd{,} \hlstr{"Estimate"}\hlstd{],}
    \hlkwc{photo} \hlstd{= fitIntrnPhoto}\hlopt{$}\hlstd{lsmeans.table[}\hlnum{1}\hlopt{:}\hlnum{16}\hlstd{,} \hlstr{"Estimate"}\hlstd{])}

  \hlstd{traitPC} \hlkwb{<-} \hlkwd{prcomp}\hlstd{(popMeans,} \hlkwc{center} \hlstd{= T,} \hlkwc{scale.} \hlstd{= T)}
  \hlstd{focClim}\hlopt{$}\hlstd{PC1} \hlkwb{<-} \hlstd{traitPC}\hlopt{$}\hlstd{x[,} \hlstr{"PC1"}\hlstd{]}

@@

\subsection*{Selective agents and environmental correlates}

As with previous studies in \textit{Mimulus} and many other species [CITES], latitude \textit{per se} predicted trait variation more than many obvious environmental variables (e.g. temperature or precipitation) that covary with latitude. We used Random Forest regression \citep{Liaw_Wiener_2002} to identify putative climatic factors underlying trait-latitude associations in \textit{M. cardinalis}. We did this by looking for overlap between climatic variables that best predict latitude of \textit{M. cadinalis} populations and climatic variables that best predict trait variation across our 16 focal populations. We used a representative set of 178 recent (since 2000) known \textit{M. cardinalis} occurences. These occurences were thinned by 50\% to correct for uneven sampling from a comprehensive set of herbarium records and an exhaustive field survey in 2010-11 \citep{Angert_ENM}. For each occurence, we used a 90m digital elevation model from HydroSHEDS \citep{Lehner_etal_2006} to extract elevation. Monthly interpolated climate layers were calculated using ClimateWNA \citep{Wang_etal_2012}, which accurately downscales climate data specifically for the rugged topography of western North America. For each occurence, we calculated bioclimatic variables using the biovars function in the R package \pkg{dismo} \citep{Hijmans_etal_2014}. In total, we included X environmental variables from ClimateWNA and 17? bioclimatic variables (Table~\ref{table:TableS_}). For each variable, we calculated both a 30-year normal by averging annual values between 1981 and 2010 and 30-year coefficient of variation, a standardized metric of interannual climatic variation). Temperatures were converted to Kelvin to be on an interval scale appropriate for calculating the coefficient of variation.

Selection at given site might not reflect simply the local environment, but rather the average environment in a surrounding region, since alleles will experience selection across populations linked by migration. We therefore calculated spatially averaged \cdm{maybe spatially-integrated is better term?} climate means and coefficients of variation. We sampled climate at 1000 random points (at 90-m resolition) within a 10 km buffer around focal populations. Since \textit{M. cardinalis} is found exclusively in riparian areas, we only selected points along streams using the National Hydrogeoraphy Dataset \citep{NHD}. Climatic means and CVs were weighted by the predicted suitability of each point, using ENM models from \cite{Angert_ENM}.

To identify climatic variables that were closely associated with latitude in \textit{M. cardinalis}, we used a "Variable Selection Using Random Forest" (VSURF) algorithm in the R \pkg{VSURF} version 0.8.2 \citep{Genuer_etal_2014}. In this algorithm, climatic variables are regressed against latitude, and the most important variables were selected after a three-stage selection process that progressively excludes unimportant variables.

Predictions: looked for climatic variables (means or CVs) that were strong predictors of both population latitudes (from all card pops) and trait variation in 16 focal popultions. If spatial average environment is important, then expect greater predictive power and closer association with latitude-predictors than point averages.

Evaluated fit on test set (correlation between predicted versus actual latitude) and on pseudoabsence set.
, Despite this common, and long-standing pattern, only certain traits In particular, adaptation to the local abiotic environment is generally thought to be the major cause of natural selection. Physiology, the study of organismal function, connects fitness to the abiotic environment, yet we actually know little about the physiological basis of adaptation to different environments within a species. To address this question, we looked at physiological variation across a broad latitudual gradient within \textit{Mimulus cardinalis}...

% Methods for spatial-average selection
For 16 focal populations, I took the average climate within a 10 km buffer, clipped to streams based on the National Hydrological Database \citep{NHD} weighted by climatic suitability determined [multimodel average/ensemble?] from ecological niche modeling \citep{Angert_ENM}.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(VSURF)}
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required package: randomForest\\\#\# randomForest 4.6-10\\\#\# Type rfNews() to see new features/changes/bug fixes.\\\#\# Loading required package: rpart\\\#\# Loading required package: doParallel\\\#\# Loading required package: foreach\\\#\# Loading required package: iterators\\\#\# Loading required package: parallel}}\begin{alltt}
  \hlcom{# Load VSURF results of climatic variables associated with latitude at cardinalis occurence points}
  \hlcom{# Note that occurences have been randomly thinned to account for variation in sampling effort}
  \hlkwd{load}\hlstd{(}\hlkwd{paste}\hlstd{(pathDat,} \hlstr{"/clim2lat_fit_t1.RData"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{))} \hlcom{# fit_t1}
  \hlstd{vsurfLat} \hlkwb{<-} \hlstd{fit_t1}

        \hlcom{# Load climVars}
        \hlkwd{load}\hlstd{(}\hlkwd{paste}\hlstd{(pathDat,} \hlstr{"/ExploratoryCimateVariables.RData"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{))}

  \hlcom{# Figure of variable importance for latitude}
  \hlkwd{pdf}\hlstd{(}\hlkwd{paste}\hlstd{(pathFig,} \hlstr{"/Figure_clim2lat_imp.pdf"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlnum{4}\hlstd{,} \hlnum{5}\hlstd{)}
  \hlkwd{par}\hlstd{(}\hlkwc{mar} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{5}\hlstd{,} \hlnum{6}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{1}\hlstd{))}
  \hlkwd{plot}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlkwd{ceiling}\hlstd{(vsurfLat}\hlopt{$}\hlstd{ord.imp}\hlopt{$}\hlstd{x)[}\hlnum{1}\hlstd{]),}
                \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred)),} \hlkwc{axes} \hlstd{= F,} \hlkwc{frame.plot} \hlstd{= T,}
                \hlkwc{xlab} \hlstd{=} \hlstr{""}\hlstd{,} \hlkwc{ylab} \hlstd{=} \hlstr{""}\hlstd{)}
        \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"Climate-Latitude\textbackslash{}nImportance"}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{4}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{)}
  \hlkwa{for} \hlstd{(i} \hlkwa{in} \hlnum{1}\hlopt{:}\hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred))}
  \hlstd{\{}
     \hlkwd{lines}\hlstd{(}\hlkwc{x} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{1}\hlstd{,} \hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred)),} \hlkwc{y} \hlstd{=} \hlkwd{c}\hlstd{(i, i),} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{)}
  \hlstd{\}}
  \hlkwd{points}\hlstd{(vsurfLat}\hlopt{$}\hlstd{ord.imp}\hlopt{$}\hlstd{x[}\hlnum{1}\hlopt{:}\hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred)],}
    \hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred)}\hlopt{:}\hlnum{1}\hlstd{,} \hlkwc{pch} \hlstd{=} \hlnum{21}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"black"}\hlstd{,} \hlkwc{bg} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{)}
        \hlcom{# mtext(climVars[vsurfLat$varselect.pred], side = 2, }
    \hlcom{# at = length(vsurfLat$varselect.pred):1, las = 1, line = 1)}
        \hlkwd{axis}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
        \hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\begin{alltt}
  \hlcom{# Variable selection using random forests (VSURF)}
  \hlstd{linmod.PC1} \hlkwb{<-} \hlkwd{as.formula}\hlstd{(}\hlkwd{paste}\hlstd{(}\hlstr{"PC1 ~ "}\hlstd{,} \hlkwd{paste}\hlstd{(climVars,} \hlkwc{collapse} \hlstd{=} \hlstr{" + "}\hlstd{),} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{))}
  \hlkwd{set.seed}\hlstd{(}\hlnum{69647}\hlstd{)}
  \hlstd{vsurfPC1} \hlkwb{<-} \hlkwd{VSURF.parallel}\hlstd{(linmod.PC1,} \hlkwc{data} \hlstd{= focClim[,} \hlkwd{c}\hlstd{(}\hlstr{"PC1"}\hlstd{, climVars)],}
    \hlkwc{ncores} \hlstd{=} \hlnum{3}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in VSURF.parallel.formula(linmod.PC1, data = focClim[, c("{}PC1"{}, : VSURF with a formula-type call outputs selected variables\\\#\# which are indices of the input matrix based on the formula:\\\#\# you may reorder these to get indices of the original data}}\begin{alltt}
  \hlcom{# Plot most important climatic predictor versus PC1}
  \hlkwd{pdf}\hlstd{(}\hlkwd{paste}\hlstd{(pathFig,} \hlstr{"/Figure_bio16cva_v_Lat.pdf"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlnum{5}\hlstd{,} \hlnum{5}\hlstd{)}
  \hlkwd{par}\hlstd{(}\hlkwc{mar} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{5}\hlstd{,} \hlnum{5}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{1}\hlstd{))}
  \hlkwd{plot}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva, focClim}\hlopt{$}\hlstd{PC1,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0.25}\hlstd{,} \hlnum{0.55}\hlstd{),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{4}\hlstd{,} \hlnum{4}\hlstd{),} \hlkwc{axes} \hlstd{= F,}
    \hlkwc{frame.plot} \hlstd{= T,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlab} \hlstd{=} \hlstr{""}\hlstd{,} \hlkwc{ylab} \hlstd{=} \hlstr{""}\hlstd{)}
  \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"Precipitation of Wettest Quarter"}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{)}
  \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"(Coefficient of variation)"}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{4}\hlstd{)}
  \hlkwd{title}\hlstd{(}\hlkwc{ylab} \hlstd{=} \hlkwd{substitute}\hlstd{(}\hlkwd{plain}\hlstd{(Principal}\hlopt{~}\hlstd{Component}\hlopt{~}\hlnum{1}\hlstd{)}\hlopt{~}\hlkwd{group}\hlstd{(}\hlstr{"("}\hlstd{, x,} \hlstr{")"}\hlstd{),}
    \hlkwd{list}\hlstd{(}\hlkwc{x} \hlstd{= pve)))}
  \hlkwd{axis}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
  \hlkwd{axis}\hlstd{(}\hlnum{2}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlopt{-}\hlnum{4}\hlstd{,} \hlnum{4}\hlstd{,} \hlnum{2}\hlstd{),} \hlkwc{las} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
  \hlstd{fitBio16cva} \hlkwb{<-} \hlkwd{lm}\hlstd{(PC1} \hlopt{~} \hlstd{bio16_cva,} \hlkwc{data} \hlstd{= focClim)}

  \hlcom{# polygon of confidence intervals}
  \hlstd{x} \hlkwb{<-} \hlkwd{seq}\hlstd{(}\hlkwd{min}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva),} \hlkwd{max}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva),} \hlkwc{l} \hlstd{=} \hlnum{1e3}\hlstd{)}
  \hlstd{u} \hlkwb{<-} \hlkwd{predict}\hlstd{(fitBio16cva,} \hlkwc{new} \hlstd{=} \hlkwd{data.frame}\hlstd{(}\hlkwc{bio16_cva} \hlstd{= x))}
  \hlstd{s} \hlkwb{<-} \hlkwd{sqrt}\hlstd{(}\hlkwd{sapply}\hlstd{(x,} \hlkwa{function}\hlstd{(}\hlkwc{X}\hlstd{)} \hlkwd{t}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{, X))} \hlopt{%*%} \hlkwd{vcov}\hlstd{(fitBio16cva)} \hlopt{%*%} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{, X)))}
  \hlstd{confInt} \hlkwb{<-} \hlkwd{data.frame}\hlstd{(}\hlkwc{lowerCI} \hlstd{=} \hlkwd{qnorm}\hlstd{(}\hlnum{0.025}\hlstd{, u, s),} \hlkwc{upperCI} \hlstd{=} \hlkwd{qnorm}\hlstd{(}\hlnum{0.975}\hlstd{, u, s))}
  \hlkwd{polygon}\hlstd{(}\hlkwd{c}\hlstd{(x,} \hlkwd{rev}\hlstd{(x)),} \hlkwd{c}\hlstd{(confInt}\hlopt{$}\hlstd{lowerCI,} \hlkwd{rev}\hlstd{(confInt}\hlopt{$}\hlstd{upperCI)),}
    \hlkwc{col} \hlstd{=} \hlstr{"grey80"}\hlstd{,} \hlkwc{border} \hlstd{=} \hlnum{NA}\hlstd{)}
  \hlkwd{lines}\hlstd{(x, confInt}\hlopt{$}\hlstd{lowerCI,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{lty} \hlstd{=} \hlnum{2}\hlstd{)}
  \hlkwd{lines}\hlstd{(x, confInt}\hlopt{$}\hlstd{upperCI,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{lty} \hlstd{=} \hlnum{2}\hlstd{)}
  \hlkwd{lines}\hlstd{(}\hlkwd{range}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva),} \hlkwd{range}\hlstd{(}\hlkwd{predict}\hlstd{(fitBio16cva)),} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{)}
  \hlkwd{points}\hlstd{(focClim}\hlopt{$}\hlstd{bio16_cva, focClim}\hlopt{$}\hlstd{PC1,} \hlkwc{pch} \hlstd{=} \hlnum{21}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"black"}\hlstd{,} \hlkwc{bg} \hlstd{= primShade0,}
    \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{)}
  \hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\begin{alltt}
  \hlcom{# Overlap between latitude predictors and phenotype predictors}
  \hlstd{imp2} \hlkwb{<-} \hlstd{climVars[vsurfPC1}\hlopt{$}\hlstd{varselect.pred]}
  \hlstd{nImpPC1} \hlkwb{<-} \hlkwd{length}\hlstd{(imp2)}

  \hlstd{vsurfLat}\hlopt{$}\hlstd{varselect.pred}
\end{alltt}
\begin{verbatim}
##  [1] 45 43 42 20 47 41 46 39 19 13
\end{verbatim}
\begin{alltt}
  \hlstd{imp1} \hlkwb{<-} \hlstd{climVars[vsurfLat}\hlopt{$}\hlstd{varselect.pred]}
  \hlstd{nImpLat} \hlkwb{<-} \hlkwd{length}\hlstd{(imp1)}

  \hlcom{# Figure of variable importance for traits}
        \hlkwd{pdf}\hlstd{(}\hlkwd{paste}\hlstd{(pathFig,} \hlstr{"/Figure_clim2pc1_imp.pdf"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlnum{4}\hlstd{,} \hlnum{5}\hlstd{)}
        \hlkwd{par}\hlstd{(}\hlkwc{mar} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{5}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{6}\hlstd{))}

        \hlkwd{plot}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.3}\hlstd{),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{, nImpLat),}
                \hlkwc{axes} \hlstd{= F,} \hlkwc{frame.plot} \hlstd{= T,} \hlkwc{xlab} \hlstd{=} \hlstr{""}\hlstd{,} \hlkwc{ylab} \hlstd{=} \hlstr{""}\hlstd{)}
        \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"Climate-Trait PC1\textbackslash{}nImportance"}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{4}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{)}
        \hlkwa{for} \hlstd{(i} \hlkwa{in} \hlstd{(nImpLat}\hlopt{:}\hlstd{(nImpLat} \hlopt{-} \hlstd{nImpPC1} \hlopt{+} \hlnum{1}\hlstd{)))}
        \hlstd{\{}
                \hlkwd{lines}\hlstd{(}\hlkwc{x} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{100}\hlstd{,} \hlnum{100}\hlstd{),} \hlkwc{y} \hlstd{=} \hlkwd{c}\hlstd{(i, i),} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{)}
        \hlstd{\}}
        \hlkwd{points}\hlstd{(vsurfPC1}\hlopt{$}\hlstd{ord.imp}\hlopt{$}\hlstd{x[}\hlnum{1}\hlopt{:}\hlstd{nImpPC1], nImpLat}\hlopt{:}\hlstd{(nImpLat} \hlopt{-} \hlstd{nImpPC1} \hlopt{+} \hlnum{1}\hlstd{),}
                \hlkwc{pch} \hlstd{=} \hlnum{21}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"black"}\hlstd{,} \hlkwc{bg} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{)}
        \hlcom{# mtext(climVars[vsurfPC1$varselect.pred], side = 4, las = 1, line = 1, }
  \hlcom{#  at = nImpLat:(nImpLat - nImpPC1 + 1), }
        \hlcom{#	font = ifelse(vsurfPC1$varselect.pred %in% vsurfLat$varselect.pred,	2, 1))}
        \hlkwd{axis}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.3}\hlstd{,} \hlnum{0.1}\hlstd{))}
  \hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{table}[ht]
   \centering
   \topcaption{Climatic variables}
   \begin{tabular}{@{} ll @{}}
      \toprule
  Climate variable & Abbreviation \\
      \midrule
  % climateWNA VARIABLES:
	DD\_0	& degree-days below 0\celsius (chilling degree-days)  \\
	DD5	  & degree-days above 5\celsius (growing degree-days)   \\
	DD\_18	& degree-days below 18\celsius (heating degree-days)  \\
	DD18	& degree-days above 18\celsius (cooling degree-days)  \\
	NFFD	& number of frost-free days                           \\
	PAS	  & precipitation as snow (mm) between August in previous year and July in current  \\
	Eref	& Hargreaves reference evaporation (mm) \\
	CMD	  & Hargreaves climativ moisture deficit (mm) \\
	MAR   &	mean annual solar radiation (NOTE: removing because too many missing values) \\
	RH    &	mean annual relative humidity \\
  % BIOCLIM VARIABLES:
  bio1	&	Annual Mean Temperature	\\
	bio2	&	Mean Diurnal Range (Mean of monthly (max temp - min temp))	\\
	bio3	&	Isothermality (bio2/bio7) (* 100)	\\
	bio4	&	Temperature Seasonality (standard deviation *100)	\\
	bio5	&	Max Temperature of Warmest Month	\\
	bio6	&	Min Temperature of Coldest Month	\\
	bio7	&	Temperature Annual Range (bio5-bio6)	\\
	bio8	&	Mean Temperature of Wettest Quarter	\\
	bio9	&	Mean Temperature of Driest Quarter	\\
	bio10	&	Mean Temperature of Warmest Quarter	\\
	bio11	&	Mean Temperature of Coldest Quarter	\\
	bio12	&	Annual Precipitation	\\
	bio15	&	Precipitation Seasonality (Coefficient of Variation)	\\
	bio16	&	Precipitation of Wettest Quarter	\\
	bio17	&	Precipitation of Driest Quarter	\\
	bio18	&	Precipitation of Warmest Quarter	\\
	bio19	&	Precipitation of Coldest Quarter	\\
	    \bottomrule
   \end{tabular}
\end{table}

%--------------------------------------------------
% Results
%--------------------------------------------------

\section*{Results}

\subsection*{Coordinated latitudinal clines in germination, growth, and photosynthesis}

Genetic differences between populations affecting originsmal function and performance point to traits that may be involved in local adaptation. Using a common garden design, we identified strong genetic differences in germination, growth, and photosynthetic rate among populations of \textit{M. cardinalis} (Table~\ref{table:Table_AnovaSummary}). A single principal component captured 74.2 %$\%$ of the trait variation among populations, defining an axis of variation from fast to slow growth (Fig~\ref{fig:Fig_PC1vLat}). As we explain below, intrinsic differences between populations in terms of plant function (photosynthesis) and performance (growth) contrasted greatly with little variation in plasticity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of Population, Treatment, Population x Treatment interactions for varies traits
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[ht]
   \centering
   \topcaption{Population, treatment effects}
   \begin{tabular}{@{} llllllll @{}}
      \toprule
                                   & Germination & Leaf expansion & Stem elongation & Photosynthesis & Intrin. Photo & Mortality \\
                                   & survreg     & lmer           & lmer            & lmer           & lmer          & glm \\
      \midrule
  Population                       &
    ***  &
    *** &
    *** &
    *** & 
    *** & 
    *** & \\
  Temperature                      &
    NA                                                          &
    ***    &
    *** &
    *** & 
     &
    *** & \\
  Water                            &
    NA                                                          &
    ***   &
    ***   &
    *** & 
     &     
    *** & \\
  Pop $\times$ Temp                &
    NA                                                          &
     &
     &
    * & 
     &     
    * & \\
  Pop $\times$ Water               &
     NA                                                          &
    * &
     &
     & 
     &     
     & \\
  Temp $\times$ Water              &
    NA                                                          &
     &
    *** &
     & 
     &     
    *** & \\
  Pop $\times$ Temp $\times$ Water &
    NA                                                          &
     &
     &
     & 
     &     
     & \\
      \bottomrule
   \end{tabular}
   \label{table:Table_AnovaSummary}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure of latitude versus PC1 (growth axis)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[h!]
	\centerline{\includegraphics[width=1\textwidth]{Figures/Figure_PC1vLat.pdf}}
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[Southern populations grow faster]{CAPTION}
	\label{fig:Fig_PC1vLat}
\end{figure}

\subsection*{Remarkably little evidence for variation in plasticity}

>>>>

\documentclass[11pt, oneside]{article}

@@

%
% Start document
%

\begin{document}
\maketitle
\listoffigures
\listoftables

@@

\subsection*{Principal components of germination, growth, and photosynthesis}
[maybe this goes in Results?]
We summarized population-level coefficients, after factoring out Treatment and other effects, using principal components. 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
  \hlstd{popMeans} \hlkwb{<-} \hlkwd{data.frame}\hlstd{(}
    \hlkwc{germ} \hlstd{=} \hlkwd{c}\hlstd{(}\hlkwd{coef}\hlstd{(fitGerm)[}\hlnum{1}\hlstd{],} \hlkwd{coef}\hlstd{(fitGerm)[}\hlnum{1}\hlstd{]} \hlopt{+} \hlkwd{coef}\hlstd{(fitGerm)[}\hlnum{2}\hlopt{:}\hlnum{16}\hlstd{]),}
    \hlkwc{LER} \hlstd{= fitLER}\hlopt{$}\hlstd{lsmeans.table[}\hlnum{1}\hlopt{:}\hlnum{16}\hlstd{,} \hlstr{"Estimate"}\hlstd{],}
    \hlkwc{SER} \hlstd{= fitSER}\hlopt{$}\hlstd{lsmeans.table[}\hlnum{1}\hlopt{:}\hlnum{16}\hlstd{,} \hlstr{"Estimate"}\hlstd{],}
    \hlkwc{photo} \hlstd{= fitIntrnPhoto}\hlopt{$}\hlstd{lsmeans.table[}\hlnum{1}\hlopt{:}\hlnum{16}\hlstd{,} \hlstr{"Estimate"}\hlstd{])}

  \hlstd{traitPC} \hlkwb{<-} \hlkwd{prcomp}\hlstd{(popMeans,} \hlkwc{center} \hlstd{= T,} \hlkwc{scale.} \hlstd{= T)}
  \hlstd{focClim}\hlopt{$}\hlstd{PC1} \hlkwb{<-} \hlstd{traitPC}\hlopt{$}\hlstd{x[,} \hlstr{"PC1"}\hlstd{]}
  \hlstd{focClimSA}\hlopt{$}\hlstd{PC1} \hlkwb{<-} \hlstd{traitPC}\hlopt{$}\hlstd{x[,} \hlstr{"PC1"}\hlstd{]}

@@
